Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-07-04 WSSSPE2_report/WSSSPE2_review.tex
Section 7.1.4: minor changes.

Subgroup B then focused on actions it could take. It discussed development of a
white paper that describes a matrix approach to training (multi-day, multi-week,
semester). The white paper might include a survey of existing techniques. There
are many, some dating back many years, for example the Interuniversity
Consortium for Political and Social Research (ICPSR) and various summer
institutes. The white paper could include a call for a comprehensive assessment
of these techniques. We need to think carefully about the right venue for such a
white paper, where would it have the most impact. The subgroup believes it would
need to approach editors directly to ascertain this.

The group felt that training in techniques that promote sustainability has a
range of benefits: career paths, educated reviewers, reproducible science and
more. There is some information on how that has been approached and assessed,
but more is needed. The group felt that this training is undervalued and that it
is important to communicate the return on investment -- both individual ROI
(skills that make scientists more effective and more marketable) and funder ROI
(better use of taxpayer funds, research more likely to be reproducible because
sustainable software exists, better trained reviewers).

>>>>

Subgroup B then focused on actions it could take. It discussed development of a
white paper that describes a matrix approach to training (multi-day, multi-week,
semester). The white paper might include a survey of existing techniques. There
are many, some dating back many years, for example the Interuniversity
Consortium for Political and Social Research (ICPSR) and various summer
institutes. The white paper could include a call for a comprehensive assessment
of these techniques. We need to think carefully about the right venue for such a
white paper, where it would have the most impact. The subgroup believes it would
need to approach editors directly to ascertain this.

The group felt that training in techniques that promote sustainability has a
range of benefits: career paths, educated reviewers, reproducible science, and
more. There is some information on how that has been approached and assessed,
but more is needed. The group felt that this training is undervalued and that it
is important to communicate the return on investment (ROI) -- both individual ROI
(skills that make scientists more effective and more marketable) and funder ROI
(better use of taxpayer funds; research more likely to be reproducible because
sustainable software exists; better trained reviewers).
